### 2007-01-17 Documentation/appendix.tex
*** empty log message ***

\section*{Superbeam experiments}
\subsection*{T2K -- {\tt T2K.glb}}

@@

Fermi Motion as is described in more detail in~\cite{Huber:2002mx}. The treatment of systematics is similar to
\cite{Ishitsuka:2005qi}. The following rules are defined within {\tt T2K.glb}:  

@@

\section*{Reactor experiments}
\subsection*{Small reactor experiment -- {\tt Reactor1.glb}}

@@

\section*{Beta beam experiments}
\subsection*{CERN-Fr\'{e}jus baseline scenario -- {\tt BB\_100.glb}}

@@

A variable $\beta$-beam scenario involving a megaton Water Cerenkov detector can be simulated with the file 
{\tt BBvar\_WC.glb}. The basic file was used within \cite{Huber:2005jk}. This reference
should be cited if the file {\tt BBvar\_WC.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BBvar\_WC.glb}, the following additional files are required:
\bi
\item {\tt BckgMig\_var.dat} (migration matrix -- background)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\item {\tt XQE.dat} (quasi elastic cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt gammafactor} (acceleration factor $\gamma$)
\item {\tt EXP\_FACTOR} (parameter of ion decay scaling)
\item {\tt baselinefactor} (baseline parameter L/$\gamma\,\left[\mathrm{km}\right]$)
\ei
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=${\tt gammafactor} for both types of isotopes and
$(100/\gamma)^\alpha\cdot2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $(60/\gamma)^\alpha\cdot5.8\cdot10^{18}$ $^{6}$He decays per year are assumed where $\alpha$~=~{\tt
EXP\_FACTOR} is a parameter that describes ion decay scaling. As default value {\tt EXP\_FACTOR=0} should be chosen.
See \cite{Huber:2005jk} for a detailed discussion of this parameter. The baseline is
L~=~{\tt baselinefactor}$\cdot\gamma$~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The appearance measurement involves the total rates data from all CC events and the spectral data
from the QE sample with a free normalization at an energy resolution of $\mathrm{\sigma_e=0.085GeV}$ due to the
Fermi Motion identical to the treatment of systematics within the \TtoK\ and \TtoHK\ files. The following rules are defined within {\tt BBvar\_WC.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{QE}}$ & \hspace{6cm} & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored -- Spectrum} & & \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{QE}$ & & 10.0 & $10^{-4}$ \\
 & & & & \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$
\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored -- Total Rates} & & \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$
\\ \hline \hline\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{QE}}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored -- Spectrum} & & \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{QE}$ & &
10.0 & $10^{-4}$ \\
 & & & & \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $^6$He stored -- Total Rates} & & \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & &
0.025 & $10^{-4}$ \\
 & & & & \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

\section*{Neutrino factory experiments}
\subsection*{Standard neutrino factory -- {\tt NFstandard.glb}}

>>>>

\section{Superbeam experiments}
\subsection*{T2K -- {\tt T2K.glb}}

@@

Fermi Motion. The normalization of the QE samples is kept free in order to avoid double counting of events since all QE
events are also contained in the CC samples. The free normalization is introduced within a rule with the line 
{\tt \@signalerror = 10.:0.0001}. In case of systematics switched on the systematics functions {\tt chiSpectrumTilt}
for the QE sample and {\tt chiTotalRatesTilt} for the CC sample are used. However, for systematics switched off, only the
systematics function for the CC sample is changed to {\tt chiNoSysTotalRates}, but the systematics function for the QE
sample stays {\tt chiSpectrumTilt}. Note, that otherwise the free normalization would be swiched off and all events from
the QE sample would be counted twice. A detailed discussion of this QE/CC sample splitting can be found in~\cite{Huber:2002mx}. 
For the disappearance channels only the QE sample is used since statistics is already quite large and a treatment like for the
appearance channels would only shlightly modify the results. The quantitative treatment of systematics is similar to \cite{Ishitsuka:2005qi}. The following rules are 
defined within {\tt T2K.glb}:  

@@

\section{Reactor experiments}
\subsection*{Small reactor experiment -- {\tt Reactor1.glb}}

@@

\section{Beta beam experiments}
\subsection*{CERN-Fr\'{e}jus baseline scenario -- {\tt BB\_100.glb}}

@@

A variable $\beta$-beam scenario involving a megaton Water Cerenkov detector can be simulated with the file 
{\tt BBvar\_WC.glb}. The basic file was used within \cite{Huber:2005jk}. This reference
should be cited if the file {\tt BBvar\_WC.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BBvar\_WC.glb}, the following additional files are required:
\item {\tt BckgMig\_var.dat} (migration matrix -- background)
and the values of the following {\sf AEDL}-Variables have to be set:
\item {\tt gammafactor} (acceleration factor $\gamma$)
\item {\tt EXP\_FACTOR} (parameter of ion decay scaling)
\item {\tt baselinefactor} (baseline parameter L/$\gamma\,\left[\mathrm{km}\right]$)
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=${\tt gammafactor} for both types of isotopes and
$(100/\gamma)^\alpha\cdot2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $(60/\gamma)^\alpha\cdot5.8\cdot10^{18}$ $^{6}$He decays per year are assumed where $\alpha$~=~{\tt
EXP\_FACTOR} is a parameter that describes ion decay scaling. As default value {\tt EXP\_FACTOR=0} should be chosen.
See \cite{Huber:2005jk} for a detailed discussion of this parameter. The baseline is
L~=~{\tt baselinefactor}$\cdot\gamma$~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The appearance measurement involves the total rates data from all CC events and the spectral data
from the QE sample with a free normalization at an energy resolution of $\mathrm{\sigma_e=0.085GeV}$ due to the
Fermi Motion identical to the treatment of systematics within the \TtoK\ and \TtoHK\ files. Note, that here also the systematics
function for the appearance sample is {\tt chiSpectrumTilt} in case of systematics on {\em and} off to avoid double counting of the
QE events for systematics switched off. The following rules are defined within {\tt BBvar\_WC.glb}:
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{QE}}$ & \hspace{6cm} & 0.025 & $10^{-4}$ \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored -- Spectrum} & & \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{QE}$ & & 10.0 & $10^{-4}$ \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$
\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored -- Total Rates} & & \\ \hline
Signal & $0.55 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
Background & $0.003 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$
\\ \hline \hline\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{QE}}$ & & 0.025 & $10^{-4}$ \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored -- Spectrum} & & \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{QE}$ & &
10.0 & $10^{-4}$ \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $^6$He stored -- Total Rates} & & \\ \hline
Signal & $0.75 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & &
0.025 & $10^{-4}$ \\
Background & $0.0025 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & $10^{-4}$ \\ \hline \hline

@@

\section{Neutrino factory experiments}
\subsection*{Standard neutrino factory -- {\tt NFstandard.glb}}
